Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2021-12-21 write-up/fda-recurrent.tex
Data cleaning

To address this, we use the recommendation from~\cite{Bartlett2020} and consider a method that first bootstraps a sample from the dataset and then apply multiple imputation to each bootstrap sample.  This general approach was originally proposed by~\cite{Shao1994} and~\cite{Little2002}. We suppose $B$ bootstraps and $M$ imputations per bootstrap; let $\hat \theta_{b,m}$ denote the estimator for the $m$th imputation of the $b$th bootstrap.  The point estimator is given by $(B)^{-1} \sum_{b=1}^B \hat \theta_{b}$ where $\hat \theta_b = M^{-1} \sum_{m=1}^M \hat \theta_{b,m}$. To construct the confidence interval, we require mean sum of squares with and between boostraps, i.e., $MSW = \frac{1}{B(M-1)} \sum_{b=1}^B \sum_{m=1}^M (\hat \theta_{b,m} - \hat \theta_b )^2$ and $MSB = \frac{1}{B-1} \sum_{b=1}^B M \cdot (\hat \theta_b - \hat \theta)^2$ respectively. Then the estimator of the variance of $\hat \theta$ is given by $\left( \frac{B+1}{BM} \right) MSB - MSW/M$.

>>>>

To address this, we use the recommendation from~\cite{Bartlett2020} and consider a method that first bootstraps a sample from the dataset and then apply multiple imputation to each bootstrap sample.  This general approach was originally proposed by~\cite{Shao1994} and~\cite{Little2002}. We suppose $B$ bootstraps and $M$ imputations per bootstrap; let $\hat \theta_{b,m}$ denote the estimator for the $m$th imputation of the $b$th bootstrap.  The point estimator is given by $(B)^{-1} \sum_{b=1}^B \hat \theta_{b}$ where $\hat \theta_b = M^{-1} \sum_{m=1}^M \hat \theta_{b,m}$. To construct the confidence interval, we require mean sum of squares with and between boostraps, i.e., $MSW = \frac{1}{B(M-1)} \sum_{b=1}^B \sum_{m=1}^M (\hat \theta_{b,m} - \hat \theta_b ) (\hat \theta_{b,m} - \hat \theta_b )^\top$ and $MSB = \frac{1}{B-1} \sum_{b=1}^B M \cdot (\hat \theta_b - \hat \theta)(\hat \theta_b - \hat \theta)^\top$ respectively. Then the estimator of the variance-covariance matrix of $\hat \theta$ is given by $\left( \frac{B+1}{BM} \right) MSB - MSW/M$.
